Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-10 IUI2021/paper.tex
...

Even finding the users' old documents can be sometimes difficult,
because people might use different keywords for the same thing case by case.
He might try to find a file related to ``IUI'' and fail, because he used
the term ``intelligent user interface'' for the file name.
%
Various techniques have been proposed to solve this vocabulary problem,
but not very successful enough.

@@

\subsection{Query Expansion}

@@

The vocabulary problem and the translation problem can be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file is the same,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
This kind of technique is called ``\textit{Query expansion}'', and simple query
expansion is possible if proper dictionary is provided.

@@

Query expansion is effective when simple substitution of keywords are satisfactory enough.
In the previous example, using the keyword ``delete'' in addition to ``remove'' works
for finding the manual entry.

However, it does not work for finding a document for vague topics.
For example, if you want to find a document that describes ``how to write a good paper'',
you will have little chance finding a document related to the topic.
Maybe it would be better to use keywords like ``how to persuade reviewers''.
However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
unless the expander knows the contents.

@@

Similarly, 
when we want to find a library function of a programming language, query expansion does not work.
For example, when we want to write a poker game program and
want to select five cards from the deck, what library should we use?
you want to selet randomly two items from an array in Ruby,
you can use the \texttt{sample()} method.
However, ``randomly selecting items'' and \texttt{sample} are so different, it is very hard for users to
find the method unless the manual contains words like ``randomly select''.

@@

It is even more difficult if the user wants to find information that is not easily described with keywords.
When a user wants to know what the icons on the Mac desktop mean, he might want to to 
search by saying "What is the symbol with three curved lines
\includegraphics[width=6mm,bb=0 0 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
on my computer display?
(folding fan, two black 90-degree arcs above a black circcle)

@@

@@

  When we want to provide a manual that describes how to delete a file, 
  we provide a RE like \verb*(delete|remove) (a file|data)*
  and generate all the text that match this RE.
  In this case, we can epand this RE into
  \verb|delete a file|,
  \verb|delete data|,
  \verb|remove a file|, and
  \verb|remove data|.
  and use all these strings for the search.
  Users can find this document by using fleible query like
  \verb|delete file| or
  \verb|remove data|.
  We can add descriptions in other languages, like \verb*(ファイル|データ)を(消す|(消去|削除)する)*
  A user can use a phrase like ``ファイルを消去する'' to find the manual page.

@@

  People make spelling errors all the time, and approximate pattern matching algorithm
  works quite effectively for almost all search activities.
  Using the ExpandSearch algorithm, all the expressions are expanded in advance,
  so simple approximate pattern matching algorithms can be applied for the search.
  For example, a query like ``del dta'' can be used

@@

  As we have shown before, one of the big reasons why we fail to find a document is that
  the user's search keyword does not exist in the document.
  Providing entries for {\ES} can solve the problem, but

  If the author of the document does not provide the data, it would be nice if
  other users can add the {\ES} entries.
  This strategy is very similar to writing a hands-on document for an existing document,
  but adding {\ES} entries is much easier than authoring  a document from scratch.

>>>>

Even finding the users' old documents can be sometimes difficult,
because people might use different keywords for the same thing case by case.
He might try to find a file related to ``IUI'' and fail, because he used
the term ``intelligent user interface'' for the file name.
%
Various techniques have been proposed to solve this vocabulary problem\cite{Furnas},
but not very successful enough.

@@

\subsection*{Query Expansion}

@@

The vocabulary problem and the translation problem can sometimes be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file mean the same thing,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
Techniques like this are called ``\textit{Query expansion}'',
and simple query expansion is possible if a good thesaurus is available.

@@

Query expansion is effective when simple substitution of keywords are satisfactory enough.
In the previous example, using the keyword ``delete'' in addition to ``remove'' works
for finding the manual entry.
More sophisticated query expansion techniques are widely used in various modern
information retrieval systems.

However, query expansion techniques do not work for finding a document for vague topics.
For example, if you want to find a document that describes ``how to write a good paper'',
you will have little chance finding a document related to the topic.
Maybe it would be better to use keywords like ``how to persuade reviewers''.
However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
unless the expander knows the contents.

@@

Similarly, 
when we want to find a library function of a programming language,
query expansion sometimes does not work.
For example, when we want to write a poker game program and
want to write a program that select five cards from 52 cards,
what library should we use?
you want to selet randomly two items from an array in Ruby,
you can use the \texttt{sample()} method.
However, ``randomly selecting items'' and \texttt{sample} are so different, it is very hard for users to
find the method unless the manual contains words like ``randomly select''.

@@

It is even more difficult if the user wants to find information that is not easily described with keywords.
When a user wants to know the meaning of an icon on the desktop, he might think
``What is the symbol with curved lines and a circle
\includegraphics[width=6mm,bb=0 0 225 225]{figures/fb2349ca17df1876178857566e7c68ef.png} % wifi icon
at the top of my Mac display?'',
but he cannot finding the information using these keywords in his brain.
(folding fan, two black 90-degree arcs above a black circle)

@@

We call the combination of these techniques as ``document expansion''.

@@

  When we want to provide a (flexible?) manual that describes how to delete a file,
  we expand the original document by
  providing REs like \verb*(delete|remove) (a file|data)*
  and generating all the texts that match the REs.
  In this case, we can epand this RE into
  \verb|delete a file|,
  \verb|delete data|,
  \verb|remove a file|, and
  \verb|remove data|,
  and use all these strings for the search.
  Users can find this document by using various query keywords like
  \verb|delete|, \verb|remove|, etc.
  We can add REs in other languages
  like \verb*(ファイル|データ)を(消す|(消去|削除)する)*.
  A Japanese user can use a phrase like ``ファイルを消去する'' to find the manual page.

@@

  People frequently make spelling errors,
  and approximate pattern matching algorithms
  work effectively for almost all search activities.
  Using the {\ES} algorithm, all the expressions are expanded,
  and simple approximate pattern matching algorithms work effectively.
  For example, a query like ``del dta'' will work for
  finding a document that describes how to ``delete data''.

@@

  One of the big reasons why we fail to find a document is that
  the user's search keyword does not exist in the document.
  If a user can expand the target documents by
  providing RE entries for {\ES},
  other users can use {\ES} for finding the documents.
  %
  This strategy is similar to creating an external index or
  writing a hands-on document for an existing document,
  but adding {\ES} entries is much easier and more flexible than
  authoring a document from scratch.
